\documentclass[margin,line]{res}

\usepackage{fancyhdr}
\usepackage{wasysym}
\usepackage{textcomp}
%\usepackage{hyperref}
\usepackage{url}
\usepackage{marvosym}
%\usepackage[misc]{ifsym}

%

%\usepackage[margin=1in]{geometry}
\addtolength{\textwidth}{0.20cm}
\addtolength{\evensidemargin}{0.1cm}
\addtolength{\oddsidemargin}{0.1cm}
\addtolength{\textheight}{-0.4cm}
\addtolength{\topmargin}{0.1cm}

%
%
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\small \thepage~of 6}
\fancyfoot[L]{\hspace{-3.2cm}\footnotesize Last updated: January 2018}
%\fancyfoot[L]{}
\renewcommand{\headrulewidth}{0pt} % no line
\renewcommand{\footrulewidth}{0pt}
%\fancyhfoffset{\sectionwidth}
\pagestyle{fancy}

%\oddsidemargin -.75in
%\evensidemargin -.5in
%\textwidth=5.5in
\itemsep=0in
\parsep=0in
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.15in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.10in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{$\circ$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.28in}}}{\end{list}}
\pagenumbering{arabic}


\begin{document}

\begin{center}
{\Large \hspace{-4cm} \bf Yu Zhang}
\end{center}
\vspace{-.25cm}
\begin{tabular}{@{}p{3.9in}p{3.9in}}
Department of Electrical Engineering       & \Telefon\, \texttt{831-459-2921}\\
University of California, Santa Cruz (UCSC)                           & \Letter\,  \texttt{zhangy@ucsc.edu} \\
Baskin Engineering 243, UCSC, CA 95064                       & \Mundus\, \url{people.ucsc.edu/~yzhan419/}
\end{tabular}
\vspace{.1in}
\begin{resume}
%
\vspace{0.2cm}



\section{\sc{\bf{POSITIONS}}}


Assistant Professor \hfill  07/2017 -- present\\
Department of Electrical Engineering \\
University of California, Santa Cruz 



Postdoctoral Employee \hfill  05/2017 -- 06/2017\\
Energy Analysis and Environmental Impacts Division \\
Lawrence Berkeley National Laboratory


Postdoctoral Scholar \hfill  01/2016 -- 04/2017\\
Industrial Engineering \& Operations Research Department\\
University of California, Berkeley  


Postdoctoral Associate \hfill  08/2015 -- 01/2016 \\
Department of Electrical and Computer Engineering  \\
University of Minnesota -- Twin Cities 
 
\vspace{.2cm}


\section{\sc{\bf{EDUCATION}}}

University of Minnesota -- Twin Cities (UMN)  \hfill  08/2010 -- 07/2015 \\
Ph.D. in Electrical Engineering 


Shanghai Jiao Tong University (SJTU)  \hfill  09/2007 -- 03/2010\\
M.S. in Electrical Engineering  


Wuhan University of Technology (WUT)   \hfill  09/2002 -- 07/2006\\
B.E. in Electrical Engineering 

\vspace{.2cm}



\section{\sc{\bf{RESEARCH INTERESTS}}}
\begin{list2}
\item Smart grids: Energy management, data analytics, and grid monitoring
\item Optimization: Distributed algorithms, stochastic and online optimization
\item Big data: High dimensional statistical inference and deep learning
\item Cyber-physical IoT systems: Optimal resource allocation
\end{list2}


%Emphasis on applying modern optimization theory, signal processing, and machine learning techniques
%to fundamental problems in cyber-physical systems including smart power grids and communication networks.
%Current research focuses on stochastic energy management with high-penetration renewables and energy data analytics.
%Additional thrusts include optimal resource allocation for wireless communications and geo-distributed data centers.

\vspace{.2cm}


\section{\sc{\bf{PUBLICATIONS}}} \newcounter{saveenum} 


{\bf Journal Papers}
\vspace{.2cm}

\begin{enumerate}\setcounter{enumi}{\value{saveenum}}

\item[J12.] \textbf{Y. Zhang}, R. Madani, and J. Lavaei,
``Conic Relaxations for Power System State Estimation with Line Measurements,"
\emph{IEEE Trans. on Control of Network Systems}, Mar. 2017 (accepted).


\item[J11.] S. Hu, \textbf{Y. Zhang}, X. Wang, and G. Giannakis,
``Weighted Sum-Rate Maximization for MIMO Downlink Systems Powered by Renewables,''
\emph{IEEE Trans. on Wireless Communications}, vol. 15, no. 8, pp. 5615-–5625, Aug. 2016.


\item[J10.] X. Wang, \textbf{Y. Zhang}, G. Giannakis, and S. Hu,
``Robust Smart-Grid Powered Cooperative Multipoint Systems,"
\emph{IEEE Trans. on Wireless Communications}, vol. 14, no. 11, pp. 1348-–1359, May 2016.


\item[J9.] \textbf{Y. Zhang} and G. Giannakis,
``Distributed Stochastic Market Clearing with High-Penetration Wind Power,"
\emph{IEEE Trans. on Power Systems}, vol. 31, no. 2, pp. 895--906, Mar. 2016.


\item[J8.] T. Chen, \textbf{Y. Zhang}, X. Wang, and G. Giannakis,
``Robust Workload and Energy Management for Sustainable Data Centers,''
\emph{IEEE Journal on Selected Areas in Communications}, vol. 34, no. 3, pp. 651--664, Mar. 2016.


\item[J7.]	X. Wang, \textbf{Y. Zhang}, T. Chen, and G. Giannakis,
``Dynamic Energy Management for Smart-Grid Powered Coordinated Multipoint Systems,"
\emph{IEEE Journal on Selected Areas in Communications}, vol. 34, no. 5, pp. 6188--6199, Nov. 2015.


\item[J6.] V. Kekatos, \textbf{Y. Zhang}, and G. Giannakis,
``Electricity Market Forecasting via Low-Rank Multi-Kernel Learning,"
\emph{IEEE Journal of Selected Topics in Signal Processing}, vol. 8, no. 6, pp. 1182--1193, Dec. 2014.

\item[J5.]	\textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Robust Energy Management for Microgrids With High-Penetration Renewables,"
\emph{IEEE Trans. on Sustainable Energy}, vol. 4, no. 4, pp. 944--953, Oct. 2013.

\item[J4.]	\textbf{Y. Zhang}, E. Dall'Anese, and G. Giannakis,
``Distributed Optimal Beamformers for Cognitive Radios Robust to Channel Uncertainties,"
\emph{IEEE Trans. on Signal Processing}, vol. 60, no. 12, pp. 6495--6508, Dec. 2012.

\item[J3.]	\textbf{Y. Zhang}, H.-W. Luo, and X.-L. Zhou,
``A Relay Scheduling Algorithm in Dual-Hop Wireless Networks,"
\emph{Journal of Shanghai Jiao Tong University}, vol. 45, no. 3, pp. 331--335, Mar. 2011.

\item[J2.]	\textbf{Y. Zhang}, H.-W. Luo, and W. Chen,
``Efficient Relay Beamforming Design with SIC Detection for Dual-Hop MIMO Relay Networks,"
\emph{IEEE Trans. on Vehicle Technology}, vol. 59, no. 8, pp. 4192--4197, Oct. 2010.

\item[J1.]	\textbf{Y. Zhang}, H.-W. Luo, C. Wang, and F. She,
``A Utility Function Based Low Complexity User Scheduling Algorithm for Multi-user MIMO Systems,"
\emph{Journal of Shanghai Jiao Tong University}, vol. 43, no. 7, pp. 1103--1107, Jul. 2009.


\end{enumerate}

{\bf Conference Papers}

\vspace{.2cm}

\begin{enumerate}

\item[C18.] \textbf{Y. Zhang}, R. Madani, and J. Lavaei,
``Power System State Estimation with Line Measurements,"
\emph{Proc. of 55th IEEE Conf. on Decision and Control (CDC)}, Las Vegas, NV, Dec. 2016.

\item[C17.] T. Chen, \textbf{Y. Zhang}, X. Wang, and G. Giannakis,
``Robust Geographical Load Balancing for Sustainable Data Centers,"
\emph{Proc. of Intl. Conf. on Acoustics, Speech, and Signal Process. (ICASSP)}, Shanghai, China, Mar. 2016.

\item[C16.] X. Wang, T. Chen, \textbf{Y. Zhang}, and G. Giannakis,
``Optimal Dynamic Power Management for Green Coordinated Multipoint Systems,"
\emph{Proc. of IEEE Global Commun. Conf. (Globecom)}, San Diego, CA, Dec. 2015.

\item[C15.] S. Chepuri, \textbf{Y. Zhang}, G. Leus, and G. Giannakis,
``Big Data Sketching with Model Mismatch,''
\emph{Proc. of Asilomar Conf. on Signals, Systems, and Computers (Asilomar)}, Pacific Grove, CA, Nov. 2015.

\item[C14.] S. Hu, X. Wang, \textbf{Y. Zhang}, G. Giannakis,
``Optimal Resource Allocation for Smart-Grid Powered MIMO Broadcast Channels,"
\emph{Proc. of 7th Intl Conf. on Wireless Commun. and Signal Process. (WCSP)}, Nanjing, China, Oct. 2015.

\item[C13.]	\textbf{Y. Zhang}, X. Wang, G. Giannakis, and S. Hu,
``Distributed Robust Resource Allocation for Renewable Powered Wireless Cellular Networks,"
\emph{Proc. of 3rd Intl. BlackSea Conf. on Commun. and Netw. (BlackSeaCom)}, Constanta, Romania, May 2015.

\item[C12.]	\textbf{Y. Zhang}, S.-J. Kim, and G. Giannakis,
``Short-Term Wind Power Forecasting using Nonnegative Sparse Coding,"
\emph{Proc. of 49th Conf. on Info. Sci. and Syst. (CISS)}, Baltimore, MD, Mar. 2015.

\item[C11.]	\textbf{Y. Zhang} and G. Giannakis,
``Distributed Market Clearing with Wind Generation and Large-Scale Dispatchable Loads,"
\emph{Proc. of 53rd IEEE Conf. on Decision and Control (CDC)}, Los Angeles, CA, Dec. 2014.

\item[C10.] G. Martinez, \textbf{Y. Zhang}, and G. Giannakis,
``An Efficient Primal-Dual Approach to Chance-Constrained Economic Dispatch,"
\emph{Proc. of North American Power Symp. (NAPS)}, Pullman, WA, Sep. 2014.

\item[C9.]	V. Kekatos, \textbf{Y. Zhang}, and G. Giannakis,
``Kernel Selection for Power Market Inference via Block Successive Upper Bound Minimization,"
\emph{Proc. of Intl. Conf. on Acoustics, Speech, and Signal Process. (ICASSP)},
Florence, Italy, May 2014.

\item[C8.]	\textbf{Y. Zhang} and G. Giannakis,
``Efficient Decentralized Economic Dispatch for Microgrids with Wind Power Integration,"
\emph{Proc. of 6th Annual IEEE Green Tech. (GreenTech)}, Corpus Christi, TX, Apr. 2014.

\item[C7.]	\textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Disaggregated Bundle Methods for Distributed Market Clearing in Power Networks,"
\emph{Proc. of 1st Global Conf. on Signal and Info. Processing (GlobalSIP)}, Austin, TX, Dec. 2013 (invited).

\item[C6.]	V. Kekatos, \textbf{Y. Zhang}, and G. Giannakis,
``Low-Rank Kernel Learning for Electricity Market Inference,"
\emph{Proc. of Asilomar Conf. on Signals, Systems, and Computers (Asilomar)}, Pacific Grove, CA, Nov. 2013.

\item[C5.]	\textbf{Y. Zhang} and G. Giannakis,
``Robust Optimal Power Flow with Wind Integration using Conditional Value-at-Risk,"
\emph{Proc. of 4th Intl. Conf. on Smart Grid Commun. (SGComm)}, Vancouver, Canada, Oct. 2013.

\item[C4.]	\textbf{Y. Zhang}, N. Gatsis, V. Kekatos, and G. Giannakis,
``Risk-aware Management of Distributed Energy Resources,"
\emph{Proc. of 18th Intl. Conf. on Digital Signal Process. (DSP)}, Santorini Island, Greece, Jul. 2013 (invited).

\item[C3.] \textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Risk-Constrained Energy Management with Multiple Wind Farms,"
\emph{Proc. of 4th IEEE-PES on Innovative Smart Grid Tech. (ISGT)}, Washington, D.C., Feb. 2013.

\item[C2.] \textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Robust Distributed Energy Management for Microgrids with Renewables,"
\emph{Proc. of 3rd Intl. Conf. on Smart Grid Commun. (SGComm)}, Tainan, Taiwan, Nov. 2012.

\item[C1.] \textbf{Y. Zhang}, E. Dall'Anese, and G. Giannakis,
``Distributed Robust Beamforming for MIMO Cognitive Networks,"
\emph{Proc. of Intl. Conf. on Acoustics, Speech, and Signal Process. (ICASSP)}, Kyoto, Japan, Mar. 2012.
\end{enumerate}




%{\bf Book chapters}
%
%\vspace{.5cm}
%
%
%\begin{enumerate}
%
%\item[B1.] S.-J. Kim, E. Dall'Anese, J. A. Bazerque, K. Rajawat, and G. Giannakis,
%``Advances in Spectrum Sensing and Cross-Layer Design in Cognitive Radio Networks,''
%\emph{Eurasip, E-Reference Signal Processing}, Nov. 2012.
%
%\end{enumerate}
%
%
%{\bf Research monographs}
%
%\vspace{.3cm}
%
%\begin{enumerate}
%
%\item[M1.] G. Giannakis, S.-J. Kim, and E. Dall'Anese, ``RF Cartography for Cognitive Radios: Spatio-Temporal Sensing and Resource Allocation,'' \emph{Foundations and Trends in Communications and Information Theory} (EiC S. Verd\'u),
% 2013, submitted.
%
%\end{enumerate}
%

%\vspace{.2cm}

{\bf Technical Reports}

\vspace{.2cm}

\begin{enumerate}

\item[R2.]	\textbf{Y. Zhang}, R. Madani, and J. Lavaei,
``Conic Relaxations for Power System State Estimation with Line Measurements,"
 Apr. 2017, [Online]. Available: \texttt{arxiv.org/abs/1704.00133}

\item[R1.]	\textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Robust Energy Management for Microgrids With High-Penetration Renewables,"
 Jul. 2012, [Online]. Available: \texttt{arxiv.org/abs/1207.4831}

\end{enumerate}

\vspace{.2cm}

{\bf Thesis}

\vspace{.2cm}

\begin{enumerate}


\item[T1.] \textbf{Y. Zhang}, ``Resource Management for Sustainable Power Grids and Wireless Networks: Distributed and Robust Designs,'' Ph.D. Thesis, ECE Department, University of Minnesota, Jul. 2015.\\
    Committee: Prodromos Daoutidis, Sairaj Dhople, Georgios Giannakis, and Mostafa Kaveh (chair).

\end{enumerate}

\vspace{.2cm}

{\bf Patents}

\vspace{.2cm}

\begin{enumerate}


\item[P5.] C. Xu, Y. Wu, \textbf{Y. Zhang}, H.-W. Luo, and H. Yu,
``Eight-Antenna Channel Estimation Method for OFDM Demodulating End,'' CHN invention patent,
pub. No.: CN 101667981 B (grant), 2012-10-31.

\item[P4.] \textbf{Y. Zhang}, H.-W. Luo, L. Chen, C. Xu, and W. Guan,
``A Low Complexity User Selection Method in Multiuser MIMO Broadcasting Channels,'' CHN invention patent,
pub. No.: CN 101499837 B (grant), 2012-09-05.


\item[P3.] L. Chen, H.-W. Luo, F. She, \textbf{Y. Zhang}, and J. Zhang,
``Method and Device of Space Division Multiple Address System Based on Codebook
of Optimal Quantization Error,'' CHN invention patent.
pub. No.: CN 101286756 B (grant), 2012-02-29.


\item[P2.] C. Xu, Y. Wu, \textbf{Y. Zhang}, H.-W. Luo, and H. Yu,
``Multi-User Multi-Antenna Two-Stage Limited Feedback Method,'' CHN invention patent.
pub. No.: CN 101695008 A, (app.), 2010-04-14.


\item[P1.] C. Xu, H.-W. Luo, L. Chen, \textbf{Y. Zhang}, and W. Guan,
``Method for Rapidly Matching Codebook of MIMO System Subscriber Terminal,'' CHN invention patent.
pub. No.: CN 101465684 A, (app.), 2009-06-24.


\end{enumerate}

\vspace{.3cm}



\section{\sc{\bf{HONORS \& AWARDS}}}
\begin{list2}
\item IEEE Signal Processing Society (SPS) Travel Grant, 2014
\item SIAM Student Travel Award, 2014
\item PhD Student Travel Fellowship, Dept of ECE, UMN, 2014	
\item	TCIPG Summer School Scholarship, 2013
\item	ECE Departmental Fellowship, UMN, 2010
\item	Shanghai Outstanding Graduate, 2010
\item	Merit Student of SJTU, 2009
\item	Huawei Scholarship, 2009
\item	Infineon Technologies Scholarship, 2009
\item	First-Class/Second-Class Academic Excellence Scholarship, SJTU, 2008/2007
\item	The Valedictorian at the WUT Commencement 2006
\item	Merit Student of Hubei Province, 2006
\item	Outstanding Graduate of WUT, 2005
\item	Pacemaker to Merit Student of WUT, Highest Honor (1\textperthousand), 2005
\item	Outstanding Merit Student of WUT, First-Class Scholarship, 2004
\item	Merit Student of WUT, Second-Class Scholarship, 2003
\end{list2}

\vspace{.3cm}




\section{\sc{\bf{FUNDING EXPERIENCE}}}
\begin{list2}


\item   PI for NSF-CMMI Collaborative Research: ``EAGER: Holistic Blockchain Based Platform for
Distributed and Intelligent Energy Communities,'' Feb. 2018. The proposal summary is under review (co-PI: Paras Mandal).

%\item   PI for the ARPR-E OPEN 2018 (DE-FOA-0001858): ``Smart Planning, Monitoring, and Operation for%Networked Microgrids via Deep Learning,'' Feb. 2018. Concept paper is submitted(co-PIs: Patrick Mantey and Paras Mandal).

\item   Co-PI for the 2018 CITRIS Seed Funding ``Data Analytics to Enable Sustainability for Power Systems,'' Jan. 2018. This proposal is under review (PI: Somayeh Sojoudi, co-PI: Javad Lavaei).
        
\item   Input for the NSF-CCSS proposal ``Smart-Grid Powered Green Communications
        in Heterogeneous Networks,'' Jun. 2015.
        This proposal was funded under grant number ECCS-1508993 (PI: Xin Wang, co-PI: Georgios Giannakis).

\item   Input for the NSF-CCF proposal ``From Communication to Power Networks:
        Adaptive Energy Management for Power Systems with Renewables,'' Sep. 2014.
        This proposal was funded under grant number CCF-1423316 (PI: Georgios Giannakis).

\item   Input for the NSF-CyberSEES proposal ``Tenable Power Distribution Networks,'' Sep. 2014.
        This proposal was funded under grant number CCF-1442686 (PI: Georgios Giannakis, Co-PI: Sairaj Dhople).

\item   Input for the NSF-RIPS proposal ``Distributed Power and Fuels in Rural Grids,''
        Mar. 2014 (PI: Georgios Giannakis).

\item   Input for the NSF-EPAS proposal ``Robust Energy Control for Microgrids with Renewables,''
        Oct. 2012 (PI: Georgios Giannakis).

\item   Input for the NSF-CPS proposal ``Inference and Management for the Power Grid: Distributed and Robust Designs,''
        Mar. 2012 (PI: Georgios Giannakis).
\end{list2}

\vspace{.3cm}

%\section{\sc{\bf{RESEARCH EXPERIENCE}}}
%
%\begin{list2}
%
%\item Postdoctoral Employee, LBNL, mentors: Anand Gopal \& Timothy Lipman
%\begin{list3}
%\item Proposed a novel fleet management for electric vehicle networks.
%\end{list3}
%
%\item Postdoctoral Scholar, UC Berkeley, advisor: Javad Lavaei
%\begin{list3}
%\item Proposed a novel convexification framework for solving the power system state estimation problem,
%and established its theoretical performance bound.
%\item Investigated the SDP relaxation and randomization algorithms for the optimal sensor placement problem.
%\end{list3}
%
%
%\item Postdoctoral Assoc. \& Research Asst., UMN, advisor: Georgios Giannakis
%\begin{list3}
%\item Proposed robust and stochastic resource allocation frameworks for smart-grid powered 
%complex networks of wireless communications and data centers.
%\item Developed robust regression for sketching big data with model mismatch.
%\item	Proposed novel models and algorithms for distributed robust and stochastic energy management with 
%renewable energy sources.
%\item  Proposed fast algorithms based on the bundle method for distributed market clearing with high-penetration wind power and large-scale demand response.
%\item  Devised efficient forecasting approaches for electricity prices via multi-kernel learning, and for wind generation using online dictionary learning.
%\item	Proposed optimal distributed beamforming algorithms for MIMO cognitive radios with channel uncertainties.
%\end{list3}
%
%
%
%\item Research Intern, USCRC-ABB, mentors: Mirrasoul Mousavi \& James Stoupis
%\begin{list3}
%\item	Proposed efficient occupancy sensing approaches via wireless sensor selection and localization for building automation systems.
%\end{list3}
%
%
%\item Research Student, UMN, mentor: Tom Luo
%\begin{list3}
%\item	Researched on optimal transceiver design for wireless communication networks.
%\item Studied complexity analysis and efficient algorithms for coordinated beamforming.
%\end{list3}
%
%
%
%\item Research Intern, Intel Asia-Pacific R\&D Ltd., mentor: Rongzhen Yang
%\begin{list3}
%\item	Researched on RBIR for the PHY abstraction between link level and system level.
%\item	Developed a link-level simulation platform for the IEEE 802.16m standard.
%\end{list3}
%
%
%\item Research Assistant, SJTU, advisor: Hanwen Luo
%\begin{list3}
%\item	  Proposed novel relay beamforming via successive interference cancellation.
%\item   Developed greedy relay selection and utility based low complexity user scheduling algorithms for MIMO systems.
%\end{list3}
%
%\end{list2}
%
%\vspace{.3cm}



\section{\sc{\bf{TEACHING EXPERIENCE}}}

\begin{list2}
\item EE293/183 Learning, Optim., and Control for Electric Power Syst., Winter 2018, UCSC
\item EE290 EE Graduate Seminar, Academic year 2017-2018, UCSC
\item Lecturer, IEOR 290 Control and Optim. for Power Syst., Spring 2017, 2016, UCB
\item TA, EE8581 Detection and Estimation Theory, Spring 2015, UMN
\item TA, EE3005 Fundamental of Electrical Engr., Fall 2010 \& Spring 2011, UMN
\item TA, ES320 Fundamental Circuits for Commun., Fall 2008, SJTU
\end{list2}

\vspace{.3cm}


\section{\sc{\bf{TALKS}}}

\vspace{.2cm}

\begin{list2}

\item   CROSS Symposium, UC Santa Cruz, CA, 2017. 
\item   Nicholas school of the Environment, Duke University, NC, 2017.
\item   ECE Department, Missouri University of Science and Technology, MO, 2017.
\item   EE Department, UC Santa Cruz, CA, 2017.        
\item   Department of Engineering Technology, University of Houston, TX, 2017.
\item   ECE Department, New York University, NY, 2017.   
\item   eCAL Seminar, UC Berkeley, CA, 2016.
\item   ECE Department, University of Louisville, KY, 2016.            
\item   ECE Department, Southern Illinois University, IL, 2015.
\item   Foundations of Resilient CybEr-physical Systems (FORCES), UC Berkeley, CA, 2015.
\item   WindLogics Inc., Saint Paul, MN, 2013.
\item   Honeywell, Minneapolis, MN, 2012.
\end{list2}

\vspace{.3cm}



\section{\sc{\bf{SERVICE}}}
\begin{list2}
\item Academic reviews:
\begin{list3}
\item \emph{IEEE Transactions on Power Systems}
\item \emph{IEEE Transactions on Smart Grid}
\item \emph{IEEE Transactions on Sustainable Energy}
\item \emph{IEEE Transactions on Automatic Control}
\item \emph{IEEE Transactions on Control Systems Technology}
\item \emph{IEEE Journal on Selected Areas in Communications}
\item \emph{IEEE Transactions on Signal Processing}
\item \emph{IEEE Transactions on Communications}
\item \emph{IEEE Transactions on Wireless Communications}
\item \emph{IEEE Transactions on Industrial Electronics}
\item \emph{IEEE Transactions on Vehicular Technology}
\item \emph{IEEE Transactions on Systems, Man, and Cybernetics: Systems}
\item \emph{IEEE Signal Processing Letters}
\item \emph{IEEE Wireless Communications Letters}
\item \emph{IEEE Power Engineering Letters}
\item \emph{IET Generation, Transmission \& Distribution}
\item \emph{International Journal of Electrical Power \& Energy Systems}
\item \emph{International Transactions on Electrical Energy Systems}
%\item \emph{MDPI - Energies}
\item \emph{International Journal of Sustainable Transportation}
\item \emph{Transportmetrica A: Transport Science}
\item \emph{ACM Trans. on Modeling and Performance Evaluation of Computing Systems}
\item \emph{Annals of Operations Research} 
\item \emph{Wiley Complexity}
\item \emph{IEEE Conference on Decision and Control}
\item \emph{IEEE American Control Conference}
\item \emph{IEEE Intl. Conference on Smart Grid Communications}
\item \emph{IEEE Intl.  Conference on Acoustics, Speech and Signal Processing}
\item \emph{IEEE Global Communications Conference}
\item \emph{IEEE Intl.  Workshop on Computational Advances in Multi-Sensor Adaptive Processing}
\item \emph{IEEE Intl.  Conference on Computing, Networking and Communications} 
\end{list3}
\vspace{4mm}
\item Session Chair or Technical Program Committee:
\begin{list3}
\item \emph{IEEE Global Conference on Signal and Information Processing} (2017)
\item \emph{IEEE International Conference on Smart Grid Communications} (2017, 2016)
\item \emph{IEEE Conference on Decision and Control}  (2014)
\item \emph{INFORMS Annual Meeting} (2017, 2016, 2015)
\end{list3}

\end{list2}
%


\vspace{0.4cm}

\section{\sc{\bf{MEMBERSHIP}}}

\begin{list2}
\item Institute of Electrical and Electronics Engineers (IEEE)
\item Institute for Operations Research and the Management Sciences (INFORMS)
\item The New York Academy of Sciences (NYAS)
\item Advisory Board Member of Swiss Innovation Valley (SIV)
\end{list2}

\vspace{0.4cm}




%\section{\sc{\bf{REFERENCES}}}
%%\begin{list2}
%%\item \textbf{Prof. Antonio Conejo}, \texttt{conejonavarro.1@osu.edu}, 614-292-6736, Ohio State Univ.
%%\item \textbf{Prof. Georgios Giannakis}, \texttt{georgios@umn.edu}, 612-626-7781, Univ. of Minnesota
%%%\item \textbf{Prof. Vassilis Kekatos}, \texttt{kekatos@vt.edu}, 540-231-1672, Virginia Tech.
%%\item\textbf{Prof. Javad Lavaei}, \texttt{lavaei@berkeley.edu}, 510-642-2497, UC Berkeley
%%\item \textbf{Prof. Shmuel Oren}, \texttt{oren@ieor.berkeley.edu}, 510-642-1836, UC Berkeley 
%%\end{list2}
%
%
%
%
%\begin{tabular}{@{}p{2.75in}p{2.75in}}
%\textbf{Prof. Georgios Giannakis}         	\\
%McKnight Presidential Endowed Chair  	\\
%ECE Dept., University of Minnesota 		\\
%Rm 495, 117 Pleasant St. SE               	\\
%Minneapolis, MN 55455, USA                	\\
%{\it Phone:} (612) 626-7781               	         \\
%{\it Email:} georgios@umn.edu 			\\
%
%\\ \\
%
%
%\textbf{Prof. Javad Lavaei}   			       \\
%IEOR Dept., UC Berkeley  				\\
%4121 Etcheverry Hall    					            \\
%Berkeley, CA 94720, USA  				               \\
%{\it Phone:} (510) 642-2497                    		            \\
%{\it Email:} lavaei@berkeley.edu              		   \\
%
%
%\\ \\
%
%
%\textbf{Prof. Shmuel Oren}         \\
%Earl J. Isaac Professor \\
%IEOR Dept., UC Berkeley   \\
%4135 Etcheverry Hall                \\
%Berkeley, CA 94720, USA                \\
%{\it Phone:} (510) 642-1836              \\
%{\it Email:} oren@ieor.berkeley.edu  \\
%
%
%\\ \\
%
%
%\textbf{Prof. Antonio Conejo}     \\
%ISE \& ECE Dept., Ohio State University    \\
%286 Baker Systems, 1971 Neil Ave.   \\
%Columbus, OH 43210, USA   \\
%{\it Phone:} (614) 292-6736   \\
%{\it Email:} conejonavarro.1@osu.edu   \\
%
%
%\end{tabular}

\end{resume}
\end{document}




%Prof. Sairaj Dhople      \\
%Dept. of Electrical and Computer Engr.\\
%University of Minnesota     \\
%Rm 5-115, 200 Union St. SE   \\
%Minneapolis, MN 55455, USA    \\
%{\it Phone:} (612) 624-8837    \\
%{\it Email:} sdhople@umn.edu   \\



%\vspace{1.0cm}
%
%Prof.  Nikolaos Gatsis  \\
%Dept. of Electrical and Computer Engr. \\
%University of Texas at San Antonio \\
%AET 2.356, One UTSA Circle, BSE 1.500 \\
%San Antonio, TX 78249, USA \\
%{\it Phone:}  (210) 258-5519 \\
%{\it Email:} nikolaos.gatsis@utsa.edu




%
%
%\vspace{.3cm}
%
%
%\section{\sc Personal}
%\begin{list2}
%%\item Date of birth: April 9th, 1985.
%%\item Marital status: single.
%\item Gender: male.
%\item Citizenship: Chinese.
%\item Languages: fluent in Chinese and English.
%\item Interests: tennis, swimming, climbing, and photography.
%\end{list2} 