\documentclass[margin,line]{res}

\usepackage{fancyhdr}
\usepackage{wasysym}
\usepackage{textcomp}
\usepackage[ hidelinks, colorlinks = true, urlcolor = blue]{hyperref}




\usepackage{url}
\usepackage{marvosym}
%\usepackage[misc]{ifsym}

%

%\usepackage[margin=1in]{geometry}
\addtolength{\textwidth}{0.20cm}
\addtolength{\evensidemargin}{0.1cm}
\addtolength{\oddsidemargin}{0.1cm}
\addtolength{\textheight}{-0.4cm}
\addtolength{\topmargin}{0.1cm}

%
%
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\small \thepage~of 7}
\fancyfoot[L]{\hspace{-3.2cm}\footnotesize Last updated: May 2019}
%\fancyfoot[L]{}
\renewcommand{\headrulewidth}{0pt} % no line
\renewcommand{\footrulewidth}{0pt}
%\fancyhfoffset{\sectionwidth}
\pagestyle{fancy}

%\oddsidemargin -.75in
%\evensidemargin -.5in
%\textwidth=5.5in
\itemsep=0in
\parsep=0in
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.15in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.10in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{$\circ$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.28in}}}{\end{list}}
\pagenumbering{arabic}


\begin{document}

\begin{center}
{\Large \hspace{-4cm} \bf Dr. Yu Zhang}
\end{center}
\vspace{-.25cm}
\begin{tabular}{@{}p{3.9in}p{3.9in}}
Department of Electrical and Computer Engineering       & \Telefon\, \texttt{831-459-2921}\\
Baskin School of Engineering, Room 243                        & \Letter\,  \texttt{zhangy@ucsc.edu} \\
University of California, Santa Cruz, CA 95064                       & \Mundus\, \url{people.ucsc.edu/~yzhan419/}
\end{tabular}
\vspace{.1in}
\begin{resume}
%
\vspace{0.2cm}



\section{\sc{\bf{RESEARCH INTERESTS}}}
\begin{list2}
\item Smart grids: Energy management, grid monitoring and data analytics
\item Cyber-physical IoT systems: Optimal resource allocation
\item Optimization and control: Distributed, stochastic and online optimization
\item Machine learning: High dimensional statistical inference and deep learning
\end{list2}
\vspace{.2cm}
%Emphasis on applying modern optimization theory, signal processing, and machine learning techniques
%to fundamental problems in cyber-physical systems including smart power grids and communication networks.
%Current research focuses on stochastic energy management with high-penetration renewables and energy data analytics.
%Additional thrusts include optimal resource allocation for wireless communications and geo-distributed data centers.


\section{\sc{\bf{POSITIONS}}}


Assistant Professor \hfill  07/2017 -- present\\
ECE Department, UC Santa Cruz \\
Hellman Fellow \& Crown Fellow \\
CITRIS and the Banatao Institute \\
Cyber-Physical Systems Research Center, UC Santa Cruz





Postdoctoral Employee \hfill  05/2017 -- 06/2017\\
Energy Analysis and Environmental Impacts Division \\
Lawrence Berkeley National Laboratory


Postdoctoral Scholar \hfill  01/2016 -- 04/2017\\
Industrial Engineering \& Operations Research Department\\
University of California, Berkeley  


Postdoctoral Associate \hfill  08/2015 -- 01/2016 \\
Department of Electrical and Computer Engineering  \\
University of Minnesota -- Twin Cities 
 
\vspace{.2cm}


\section{\sc{\bf{EDUCATION}}}

University of Minnesota -- Twin Cities (UMN)  \hfill  08/2010 -- 07/2015 \\
Ph.D. in Electrical Engineering 


Shanghai Jiao Tong University (SJTU)  \hfill  09/2007 -- 03/2010\\
M.S. in Electrical Engineering  (With Highest Honors)


Wuhan University of Technology (WUT)   \hfill  09/2002 -- 07/2006\\
B.E. in Electrical Engineering  (With Highest Honors)

\vspace{.2cm}




\section{\sc{\bf{PUBLICATIONS}}} \newcounter{saveenum} 

{\href{https://scholar.google.com/citations?user=mt3m9bIAAAAJ&hl=en/}{Google scholar citations 908, h-index 13, i10-index 14.}}
\vspace{.2cm}

\begin{enumerate}\setcounter{enumi}{\value{saveenum}}



\item[31.] \textbf{Y. Zhang}, R. Madani, and J. Lavaei,
``Conic Relaxations for Power System State Estimation with Line Measurements,"
\emph{IEEE Trans. on Control of Network Systems}, vol. 5, no. 3, pp. 1193-1205, Sept. 2018.


\item[30.]  A. Maqsood, \textbf{Y. Zhang}, and K. Corzine
``Optimal Rotational Load Shedding via Bilinear Integer Programming,''
\emph{Proc. of Asia-Pacific Signal and Information Processing Assoc. Annual Summit and Conf. (APSIPA ASC)}, Honolulu, Hawaii, Nov. 2018.

\item[29.] \textbf{Y. Zhang}, R. Madani, and J. Lavaei,
``Power System State Estimation with Line Measurements,"
\emph{Proc. of 55th IEEE Conf. on Decision and Control (CDC)}, Las Vegas, NV, Dec. 2016.


\item[28.] S. Hu, \textbf{Y. Zhang}, X. Wang, and G. Giannakis,
``Weighted Sum-Rate Maximization for MIMO Downlink Systems Powered by Renewables,''
\emph{IEEE Trans. on Wireless Communications}, vol. 15, no. 8, pp. 5615-–5625, Aug. 2016.


\item[27.] X. Wang, \textbf{Y. Zhang}, G. Giannakis, and S. Hu,
``Robust Smart-Grid Powered Cooperative Multipoint Systems,"
\emph{IEEE Trans. on Wireless Communications}, vol. 14, no. 11, pp. 1348-–1359, May 2016.


\item[26.] \textbf{Y. Zhang} and G. Giannakis,
``Distributed Stochastic Market Clearing with High-Penetration Wind Power,"
\emph{IEEE Trans. on Power Systems}, vol. 31, no. 2, pp. 895--906, Mar. 2016.


\item[25.] T. Chen, \textbf{Y. Zhang}, X. Wang, and G. Giannakis,
``Robust Geographical Load Balancing for Sustainable Data Centers,"
\emph{Proc. of Intl. Conf. on Acoustics, Speech, and Signal Process. (ICASSP)}, Shanghai, China, Mar. 2016.

\item[24.] T. Chen, \textbf{Y. Zhang}, X. Wang, and G. Giannakis,
``Robust Workload and Energy Management for Sustainable Data Centers,''
\emph{IEEE Journal on Selected Areas in Communications}, vol. 34, no. 3, pp. 651--664, Mar. 2016.


\item[23.] X. Wang, T. Chen, \textbf{Y. Zhang}, and G. Giannakis,
``Optimal Dynamic Power Management for Green Coordinated Multipoint Systems,"
\emph{Proc. of IEEE Global Commun. Conf. (Globecom)}, San Diego, CA, Dec. 2015.

\item[22.] S. Chepuri, \textbf{Y. Zhang}, G. Leus, and G. Giannakis,
``Big Data Sketching with Model Mismatch,''
\emph{Proc. of Asilomar Conf. on Signals, Systems, and Computers (Asilomar)}, Pacific Grove, CA, Nov. 2015.


\item[21.]	X. Wang, \textbf{Y. Zhang}, T. Chen, and G. Giannakis,
``Dynamic Energy Management for Smart-Grid Powered Coordinated Multipoint Systems,"
\emph{IEEE Journal on Selected Areas in Communications}, vol. 34, no. 5, pp. 6188--6199, Nov. 2015.

\item[20.] S. Hu, X. Wang, \textbf{Y. Zhang}, G. Giannakis,
``Optimal Resource Allocation for Smart-Grid Powered MIMO Broadcast Channels,"
\emph{Proc. of 7th Intl Conf. on Wireless Commun. and Signal Process. (WCSP)}, Nanjing, China, Oct. 2015.

\item[19.]	\textbf{Y. Zhang}, X. Wang, G. Giannakis, and S. Hu,
``Distributed Robust Resource Allocation for Renewable Powered Wireless Cellular Networks,"
\emph{Proc. of 3rd Intl. BlackSea Conf. on Commun. and Netw. (BlackSeaCom)}, Constanta, Romania, May 2015.

\item[18.]	\textbf{Y. Zhang}, S.-J. Kim, and G. Giannakis,
``Short-Term Wind Power Forecasting using Nonnegative Sparse Coding,"
\emph{Proc. of 49th Conf. on Info. Sci. and Syst. (CISS)}, Baltimore, MD, Mar. 2015.


\item[17.] V. Kekatos, \textbf{Y. Zhang}, and G. Giannakis,
``Electricity Market Forecasting via Low-Rank Multi-Kernel Learning,"
\emph{IEEE Journal of Selected Topics in Signal Processing}, vol. 8, no. 6, pp. 1182--1193, Dec. 2014.

\item[16.]	\textbf{Y. Zhang} and G. Giannakis,
``Distributed Market Clearing with Wind Generation and Large-Scale Dispatchable Loads,"
\emph{Proc. of 53rd IEEE Conf. on Decision and Control (CDC)}, Los Angeles, CA, Dec. 2014.

\item[15.] G. Martinez, \textbf{Y. Zhang}, and G. Giannakis,
``An Efficient Primal-Dual Approach to Chance-Constrained Economic Dispatch,"
\emph{Proc. of North American Power Symp. (NAPS)}, Pullman, WA, Sep. 2014.

\item[14.]	V. Kekatos, \textbf{Y. Zhang}, and G. Giannakis,
``Kernel Selection for Power Market Inference via Block Successive Upper Bound Minimization,"
\emph{Proc. of Intl. Conf. on Acoustics, Speech, and Signal Process. (ICASSP)},
Florence, Italy, May 2014.

\item[13.]	\textbf{Y. Zhang} and G. Giannakis,
``Efficient Decentralized Economic Dispatch for Microgrids with Wind Power Integration,"
\emph{Proc. of 6th Annual IEEE Green Tech. (GreenTech)}, Corpus Christi, TX, Apr. 2014.


\item[12.]	\textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Disaggregated Bundle Methods for Distributed Market Clearing in Power Networks,"
\emph{Proc. of 1st Global Conf. on Signal and Info. Processing (GlobalSIP)}, Austin, TX, Dec. 2013 (invited).

\item[11.]	V. Kekatos, \textbf{Y. Zhang}, and G. Giannakis,
``Low-Rank Kernel Learning for Electricity Market Inference,"
\emph{Proc. of Asilomar Conf. on Signals, Systems, and Computers (Asilomar)}, Pacific Grove, CA, Nov. 2013.

\item[10.]	\textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Robust Energy Management for Microgrids With High-Penetration Renewables,"
\emph{IEEE Trans. on Sustainable Energy}, vol. 4, no. 4, pp. 944--953, Oct. 2013.

\item[9.]	\textbf{Y. Zhang} and G. Giannakis,
``Robust Optimal Power Flow with Wind Integration using Conditional Value-at-Risk,"
\emph{Proc. of 4th Intl. Conf. on Smart Grid Commun. (SGComm)}, Vancouver, Canada, Oct. 2013.

\item[8.]	\textbf{Y. Zhang}, N. Gatsis, V. Kekatos, and G. Giannakis,
``Risk-aware Management of Distributed Energy Resources,"
\emph{Proc. of 18th Intl. Conf. on Digital Signal Process. (DSP)}, Santorini Island, Greece, Jul. 2013 (invited).

\item[7.] \textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Risk-Constrained Energy Management with Multiple Wind Farms,"
\emph{Proc. of 4th IEEE-PES on Innovative Smart Grid Tech. (ISGT)}, Washington, D.C., Feb. 2013.

\item[6.]	\textbf{Y. Zhang}, E. Dall'Anese, and G. Giannakis,
``Distributed Optimal Beamformers for Cognitive Radios Robust to Channel Uncertainties,"
\emph{IEEE Trans. on Signal Processing}, vol. 60, no. 12, pp. 6495--6508, Dec. 2012.

\item[5.] \textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Robust Distributed Energy Management for Microgrids with Renewables,"
\emph{Proc. of 3rd Intl. Conf. on Smart Grid Commun. (SGComm)}, Tainan, Taiwan, Nov. 2012.

\item[4.] \textbf{Y. Zhang}, E. Dall'Anese, and G. Giannakis,
``Distributed Robust Beamforming for MIMO Cognitive Networks,"
\emph{Proc. of Intl. Conf. on Acoustics, Speech, and Signal Process. (ICASSP)}, Kyoto, Japan, Mar. 2012.

\item[3.]	\textbf{Y. Zhang}, H.-W. Luo, and X.-L. Zhou,
``A Relay Scheduling Algorithm in Dual-Hop Wireless Networks,"
\emph{Journal of Shanghai Jiao Tong University}, vol. 45, no. 3, pp. 331--335, Mar. 2011.

\item[2.]	\textbf{Y. Zhang}, H.-W. Luo, and W. Chen,
``Efficient Relay Beamforming Design with SIC Detection for Dual-Hop MIMO Relay Networks,"
\emph{IEEE Trans. on Vehicle Technology}, vol. 59, no. 8, pp. 4192--4197, Oct. 2010.

\item[1.]	\textbf{Y. Zhang}, H.-W. Luo, C. Wang, and F. She,
``A Utility Function Based Low Complexity User Scheduling Algorithm for Multi-user MIMO Systems,"
\emph{Journal of Shanghai Jiao Tong University}, vol. 43, no. 7, pp. 1103--1107, Jul. 2009.


\end{enumerate}




%{\bf Book chapters}
%
%\vspace{.5cm}
%
%
%\begin{enumerate}
%
%\item[B1.] S.-J. Kim, E. Dall'Anese, J. A. Bazerque, K. Rajawat, and G. Giannakis,
%``Advances in Spectrum Sensing and Cross-Layer Design in Cognitive Radio Networks,''
%\emph{Eurasip, E-Reference Signal Processing}, Nov. 2012.
%
%\end{enumerate}
%
%
%{\bf Research monographs}
%
%\vspace{.3cm}
%
%\begin{enumerate}
%
%\item[M1.] G. Giannakis, S.-J. Kim, and E. Dall'Anese, ``RF Cartography for Cognitive Radios: Spatio-Temporal Sensing and Resource Allocation,'' \emph{Foundations and Trends in Communications and Information Theory} (EiC S. Verd\'u),
% 2013, submitted.
%
%\end{enumerate}
%

%\vspace{.2cm}

{\bf Technical Reports}

\vspace{.2cm}

\begin{enumerate}

\item[R2.]	\textbf{Y. Zhang}, R. Madani, and J. Lavaei,
``Conic Relaxations for Power System State Estimation with Line Measurements,"
 Apr. 2017, [Online]. Available: \texttt{arxiv.org/abs/1704.00133}

\item[R1.]	\textbf{Y. Zhang}, N. Gatsis, and G. Giannakis,
``Robust Energy Management for Microgrids With High-Penetration Renewables,"
 Jul. 2012, [Online]. Available: \texttt{arxiv.org/abs/1207.4831}

\end{enumerate}

\vspace{.2cm}


{\bf Preprints}

\begin{enumerate}

\item[P4.]  Fault Location in Power Distribution Systems via Deep Graph Convolutional Networks
Kunjin Chen, Jun Hu, Yu Zhang, Zhanqing Yu, and Jinliang He, 2019

\item[P3.] Scale- and Context-Aware Convolutional Non-intrusive Load Monitoring
Kunjin Chen and Yu Zhang, 2019


\item[P2.] Greening Service Capacity and Coordination in Telecom Supply Chains
Tianjian Yang, Yue-Jun Zhang, Yu Zhang, and Jiangai Tian, 2019.

\item[P1.]  Coordination of Prices, Green Efforts and Service Level in a Dynamic Supply Chain with a Sweatshop Mode
Tianjian Yang, Xiuxiu Jiang, Yu Zhang, and Yue-Jun Zhang, 2018.

\end{enumerate}

{\bf PhD Thesis}

\vspace{.2cm}

\begin{enumerate}


\item[T1.] \textbf{Y. Zhang}, ``Resource Management for Sustainable Power Grids and Wireless Networks: Distributed and Robust Designs,'' Ph.D. Thesis, ECE Department, University of Minnesota, Jul. 2015.\\
    Committee: Prodromos Daoutidis, Sairaj Dhople, Georgios Giannakis, and Mostafa Kaveh (chair).

\end{enumerate}

\vspace{.2cm}


{\bf Posters}

\vspace{.2cm}

\begin{enumerate}
\item[PO1.] J. Miao, J. Chhabra, and \textbf{Y. Zhang}, ``Medium-term Wind Power Forecasting via Recurrent Neural Networks,''
1st conference on Machine Learning in Science and Engineering, Carnegie Mellon University, Pittsburgh, PA, Jun. 6-8, 2018.

\item[PO2.] J. Miao, J. Chhabra, and \textbf{Y. Zhang}, ``Medium-term Wind Power Forecasting via Recurrent Neural Networks,''
Data Science Workshop, The Data Science Institute and the University of California, Livermore, CA, Aug 7-8, 2018.
\end{enumerate}

\vspace{.2cm}




{\bf Patents}

\vspace{.2cm}

\begin{enumerate}


\item[PA5.] C. Xu, Y. Wu, \textbf{Y. Zhang}, H.-W. Luo, and H. Yu,
``Eight-Antenna Channel Estimation Method for OFDM Demodulating End,'' CHN invention patent,
pub. No.: CN 101667981 B (grant), 2012-10-31.

\item[PA4.] \textbf{Y. Zhang}, H.-W. Luo, L. Chen, C. Xu, and W. Guan,
``A Low Complexity User Selection Method in Multiuser MIMO Broadcasting Channels,'' CHN invention patent,
pub. No.: CN 101499837 B (grant), 2012-09-05.


\item[PA3.] L. Chen, H.-W. Luo, F. She, \textbf{Y. Zhang}, and J. Zhang,
``Method and Device of Space Division Multiple Address System Based on Codebook
of Optimal Quantization Error,'' CHN invention patent.
pub. No.: CN 101286756 B (grant), 2012-02-29.


\item[PA2.] C. Xu, Y. Wu, \textbf{Y. Zhang}, H.-W. Luo, and H. Yu,
``Multi-User Multi-Antenna Two-Stage Limited Feedback Method,'' CHN invention patent.
pub. No.: CN 101695008 A, (app.), 2010-04-14.


\item[PA1.] C. Xu, H.-W. Luo, L. Chen, \textbf{Y. Zhang}, and W. Guan,
``Method for Rapidly Matching Codebook of MIMO System Subscriber Terminal,'' CHN invention patent.
pub. No.: CN 101465684 A, (app.), 2009-06-24.


\end{enumerate}

\vspace{.3cm}


\section{\sc{\bf{FUNDING EXPERIENCE}}}
\begin{list2}

\item  Lead-PI for CITRIS and the Banatao Institute 2019 Seed Fund: ``Multi-hazard risk analysis to inform distribution grid upgrades for reliability and resilience,'' Committee on Research of UC Santa Cruz, Apr. 2019.

\item  PI for the Faculty Research Grant (FRG): ``Modernizing Power Grid Infrastructure Against Extreme Natural Hazards,'' Committee on Research of UC Santa Cruz, Apr. 2019.

\item  PI for the Faculty Research Grant (FRG): ``Smart Monitoring and Predictive Learning for Sustainable Microgrids,'' Committee on Research of UC Santa Cruz, May 2018.

%\item   Co-PI for the NSF-SCC: ``Improving Economics and Quality of Life in Rural Communities by Integrated Communications and Sensors,'' 
%Feb. 2018. The proposal is under review (PI: Patrick Mantey).

%\item   PI for the ARPR-E OPEN 2018 (DE-FOA-0001858): ``Smart Planning, Monitoring, and Operation for
%Networked Microgrids via Deep Learning,'' Feb. 2018. Concept paper is under review (co-PIs: Patrick Mantey and Paras Mandal).

%\item   Co-PI for the 2018 CITRIS Seed Funding: ``Data Analytics to Enable Sustainability for Power Systems,'' Jan. 2018. This proposal is under review (PI: Somayeh Sojoudi, co-PI: Javad Lavaei).

\item   Input for the NSF-CCSS proposal ``Smart-Grid Powered Green Communications
        in Heterogeneous Networks,'' Jun. 2015.
        This proposal was funded under grant number ECCS-1508993 (PI: Xin Wang, co-PI: Georgios Giannakis).

\item   Input for the NSF-CCF proposal ``From Communication to Power Networks:
        Adaptive Energy Management for Power Systems with Renewables,'' Sep. 2014.
        This proposal was funded under grant number CCF-1423316 (PI: Georgios Giannakis).

\item   Input for the NSF-CyberSEES proposal ``Tenable Power Distribution Networks,'' Sep. 2014.
        This proposal was funded under grant number CCF-1442686 (PI: Georgios Giannakis, Co-PI: Sairaj Dhople).

\item   Input for the NSF-RIPS proposal ``Distributed Power and Fuels in Rural Grids,''
        Mar. 2014 (PI: Georgios Giannakis).

\item   Input for the NSF-EPAS proposal ``Robust Energy Control for Microgrids with Renewables,''
        Oct. 2012 (PI: Georgios Giannakis).

\item   Input for the NSF-CPS proposal ``Inference and Management for the Power Grid: Distributed and Robust Designs,''
        Mar. 2012 (PI: Georgios Giannakis).
\end{list2}

\vspace{.3cm}



\section{\sc{\bf{MEDIA COVERAGE}}}
\begin{list2}

\item  The New York Academy of Sciences: \href{https://www.nyas.org/magazines/imagining-the-next-100-years/imagining-the-next-100-years-of-science-and-technology/}{The Coming Revolution in Smart Electric Power}.

\end{list2}

\vspace{.3cm}



\section{\sc{\bf{HONORS \& AWARDS}}}
\begin{list2}
\item IEEE Signal Processing Society (SPS) Travel Grant, 2014
\item SIAM Student Travel Award, 2014
\item PhD Student Travel Fellowship, Dept of ECE, UMN, 2014	
\item	TCIPG Summer School Scholarship, 2013
\item	ECE Departmental Fellowship, UMN, 2010
\item	Shanghai Outstanding Graduate, 2010
\item	Merit Student of SJTU, 2009
\item	Huawei Scholarship, 2009
\item	Infineon Technologies Scholarship, 2009
\item	First-Class/Second-Class Academic Excellence Scholarship, SJTU, 2008/2007
\item	The Valedictorian at the WUT Commencement 2006
\item	Merit Student of Hubei Province, 2006
\item	Outstanding Graduate of WUT, 2005
\item	Pacemaker to Merit Student of WUT, Highest Honor (1\textperthousand), 2005
\item	Outstanding Merit Student of WUT, First-Class Scholarship, 2004
\item	Merit Student of WUT, Second-Class Scholarship, 2003
\end{list2}

\vspace{.3cm}


\section{\sc{\bf{TEACHING EXPERIENCE}}}

\begin{list2}
%\item Lecturer, EE180J/EE80J Advanced Renewable Energy Sources, Spring 2018, UCSC
\item EE279 \emph{Control and Optim. for Electric Power Syst.}, Winter 2018, Spring 2019, UCSC
\item EE253/CMPS250 \emph{Introduction to Info. Theory}, Spring 2019, UCSC
\item EE290 \emph{Graduate Seminar}, Academic years 2017--19, UCSC
%\item Lecturer, IEOR290 Control and Optim. for Power Syst., Spring 2016--17, UCB
%\item TA, EE8581 Detection and Estimation Theory, Spring 2015, UMN
%\item TA, EE3005 Fundamental of Electrical Engr., Fall 2010 \& Spring 2011, UMN
%\item TA, ES320 Fundamental Circuits for Commun., Fall 2008, SJTU
\end{list2}

\vspace{.3cm}


\section{\sc{\bf{TALKS}}}

\vspace{.2cm}

\begin{list2}

\item   CROSS Symposium, UC Santa Cruz, CA, 2017. 
\item   Nicholas school of the Environment, Duke University, NC, 2017.
\item   ECE Department, Missouri University of Science and Technology, MO, 2017.
%\item   EE Department, UC Santa Cruz, CA, 2017.        
\item   Department of Engineering Technology, University of Houston, TX, 2017.
\item   ECE Department, New York University, NY, 2017.   
\item   eCAL Seminar, UC Berkeley, CA, 2016.
\item   ECE Department, University of Louisville, KY, 2016.            
\item   ECE Department, Southern Illinois University, IL, 2015.
\item   Foundations of Resilient CybEr-physical Systems (FORCES), UC Berkeley, CA, 2015.
\item   WindLogics Inc., Saint Paul, MN, 2013.
\item   Honeywell, Minneapolis, MN, 2012.
\end{list2}

\vspace{.3cm}



\section{\sc{\bf{SERVICE}}}
\begin{list2}


\item Session Chair or Technical Program Committee:
\begin{list3}
\item \emph{IEEE Global Conf. on Signal and Information Processing} (2019, 2017, 2016)
\item \emph{IEEE Intl. Conf.  on Smart Grid Communications} (2017--2015)
\item \emph{IEEE Conf.  on Decision and Control}  (2014)
\item \emph{INFORMS Annual Meeting} (2017, 2016, 2015)
\end{list3}
\vspace{4mm}

\item Committee/Board Member:
\begin{list3}
\item Associate Editor, Conf. Editorial Board of IEEE Control Systems Society
\item Committee on Research of UC Santa Cruz
\item Swiss Innovation Valley
\end{list3}
\vspace{4mm}

\item Academic Reviewer:
\begin{list3}
\item \emph{IEEE Transactions on Power Systems}
\item \emph{IEEE Transactions on Smart Grid}
\item \emph{IEEE Transactions on Sustainable Energy}
\item \emph{IEEE Transactions on Automatic Control}
\item \emph{IEEE Transactions on Control Systems Technology}
\item \emph{IEEE Journal on Selected Areas in Communications}
\item \emph{IEEE Transactions on Signal Processing}
\item \emph{IEEE Transactions on Communications}
\item \emph{IEEE Transactions on Wireless Communications}
\item \emph{IEEE Transactions on Industrial Electronics}
\item \emph{IEEE Transactions on Vehicular Technology}
\item \emph{IEEE Transactions on Systems, Man, and Cybernetics: Systems}
\item \emph{IEEE Signal Processing Letters}
\item \emph{IEEE Wireless Communications Letters}
\item \emph{IEEE Power Engineering Letters}
\item \emph{IET Generation, Transmission \& Distribution}
\item \emph{International Journal of Electrical Power \& Energy Systems}
\item \emph{International Transactions on Electrical Energy Systems}
%\item \emph{MDPI - Energies}
\item \emph{International Journal of Sustainable Transportation}
\item \emph{Transportmetrica A: Transport Science}
\item \emph{ACM Trans. on Modeling and Performance Evaluation of Computing Systems}
\item \emph{Annals of Operations Research} 
\item \emph{Wiley Complexity}
\item \emph{IEEE Conference on Decision and Control}
\item \emph{IEEE American Control Conference}
\item \emph{IEEE Intl. Conference on Smart Grid Communications}
\item \emph{IEEE Intl.  Conference on Acoustics, Speech and Signal Proc.}
\item \emph{IEEE Global Communications Conference}
\item \emph{IEEE Intl.  Wrksp on Computational Advances in Multi-Sensor Adaptive Proc.}
\item \emph{IEEE Intl.  Conference on Computing, Networking and Communications} 
\end{list3}

\end{list2}
%


\vspace{0.4cm}

\section{\sc{\bf{MEMBERSHIP}}}

\begin{list2}
\item Institute of Electrical and Electronics Engineers (IEEE)
\item Society for Industrial and Applied Mathematics (SIAM)
\item Institute for Operations Research and the Management Sciences (INFORMS)
\item The New York Academy of Sciences (NYAS)
\end{list2}

\vspace{0.4cm}

%\section{\sc{\bf{CURRENT STUDENTS}}}
%
%\begin{list2}
%\item Janesh Chhabra (Junior in Computer Science), 10/2017 -- present
%\item Jian Miao (Junior in Computer Engineering), 12/2017 -- present
%%\item Aravind Patnam (Sophomore in Computer Science), 10/2017 -- present
%\end{list2}


%\section{\sc{\bf{REFERENCES}}}
%%\begin{list2}
%%\item \textbf{Prof. Antonio Conejo}, \texttt{conejonavarro.1@osu.edu}, 614-292-6736, Ohio State Univ.
%%\item \textbf{Prof. Georgios Giannakis}, \texttt{georgios@umn.edu}, 612-626-7781, Univ. of Minnesota
%%%\item \textbf{Prof. Vassilis Kekatos}, \texttt{kekatos@vt.edu}, 540-231-1672, Virginia Tech.
%%\item\textbf{Prof. Javad Lavaei}, \texttt{lavaei@berkeley.edu}, 510-642-2497, UC Berkeley
%%\item \textbf{Prof. Shmuel Oren}, \texttt{oren@ieor.berkeley.edu}, 510-642-1836, UC Berkeley 
%%\end{list2}
%
%
%
%
%\begin{tabular}{@{}p{2.75in}p{2.75in}}
%\textbf{Prof. Georgios Giannakis}         	\\
%McKnight Presidential Endowed Chair  	\\
%ECE Dept., University of Minnesota 		\\
%Rm 495, 117 Pleasant St. SE               	\\
%Minneapolis, MN 55455, USA                	\\
%{\it Phone:} (612) 626-7781               	         \\
%{\it Email:} georgios@umn.edu 			\\
%
%\\ \\
%
%
%\textbf{Prof. Javad Lavaei}   			       \\
%IEOR Dept., UC Berkeley  				\\
%4121 Etcheverry Hall    					            \\
%Berkeley, CA 94720, USA  				               \\
%{\it Phone:} (510) 642-2497                    		            \\
%{\it Email:} lavaei@berkeley.edu              		   \\
%
%
%\\ \\
%
%
%\textbf{Prof. Shmuel Oren}         \\
%Earl J. Isaac Professor \\
%IEOR Dept., UC Berkeley   \\
%4135 Etcheverry Hall                \\
%Berkeley, CA 94720, USA                \\
%{\it Phone:} (510) 642-1836              \\
%{\it Email:} oren@ieor.berkeley.edu  \\
%
%
%\\ \\
%
%
%\textbf{Prof. Antonio Conejo}     \\
%ISE \& ECE Dept., Ohio State University    \\
%286 Baker Systems, 1971 Neil Ave.   \\
%Columbus, OH 43210, USA   \\
%{\it Phone:} (614) 292-6736   \\
%{\it Email:} conejonavarro.1@osu.edu   \\
%
%
%\end{tabular}

\end{resume}
\end{document}




%Prof. Sairaj Dhople      \\
%Dept. of Electrical and Computer Engr.\\
%University of Minnesota     \\
%Rm 5-115, 200 Union St. SE   \\
%Minneapolis, MN 55455, USA    \\
%{\it Phone:} (612) 624-8837    \\
%{\it Email:} sdhople@umn.edu   \\



%\vspace{1.0cm}
%
%Prof.  Nikolaos Gatsis  \\
%Dept. of Electrical and Computer Engr. \\
%University of Texas at San Antonio \\
%AET 2.356, One UTSA Circle, BSE 1.500 \\
%San Antonio, TX 78249, USA \\
%{\it Phone:}  (210) 258-5519 \\
%{\it Email:} nikolaos.gatsis@utsa.edu




%
%
%\vspace{.3cm}
%
%
%\section{\sc Personal}
%\begin{list2}
%%\item Date of birth: April 9th, 1985.
%%\item Marital status: single.
%\item Gender: male.
%\item Citizenship: Chinese.
%\item Languages: fluent in Chinese and English.
%\item Interests: tennis, swimming, climbing, and photography.
%\end{list2} 